Artificial Neural Network based critical conditions for Dynamic Recrystallization of Medium Carbon Steel and Application

### 2023-10-03 Article.tex
Modifs based on reviewers recommandations

As the occurrence of the DRX softens the material, the deformation loads during hot deformation must be adjusted from one pass to another to have more accurate prediction of DRX.
Therefore, understanding the critical conditions for dynamic recrystallization (DRX) is important for modeling industrial processes.
However, the extent of DRX is influenced by factors such as material composition, deformation temperature, strain rate, and strain.
By optimizing the parameters, engineers can attain the desired microstructures and mechanical properties in the final product.
Various experimental techniques have been proposed by researchers to establish DRX's critical conditions such as metallographic analysis \cite{babu2022implication, khan2021interactions}.
However, this technique requires extensive sampling before and after reaching the critical deformation point at which the material experiences recovery and recrystallization processes, resulting in the formation of new grains and a decrease in the average grain size.
Additionally, the cooling phase sometimes entails phase changes (depending on the material's type) from the hot working temperature, which alter the deformed structure, rendering the metallographic analysis complex.
Hence, simpler techniques such as the development of analytical models are required to determine DRX initiation.
In this regard, multiple studies have been carried out aiming to analytically identify the initiation of DRX.
For instance, Yan Peng \eal \cite{peng2022dynamic} determined the critical strain and critical stress for the DRX's initiation based on the method proposed by Najafizadeh and Jonas \cite{Najafizadeh-2006} to establish a DRX kinetic model for the hot-rolled condition based on the relationship between the characteristic parameters of DRX and temperature and strain rate. This approach defines the critical stress required for the initiation of DRX during deformation.
According to Gottstein \eal \cite{gottstein2004prediction}, the critical strain for initiating DRX can also be predicted based on a work hardening model of dislocation density.
The onset of dynamic recrystallization (DRX) may be identified through the inflection point in the strain hardening rate $\theta(\sigma)=\frac{\partial \sigma}{\partial \varepsilon}$ where $\sigma$ is the stress and $\varepsilon$ is the strain.

The DRX phenomenon, based on the inflection point, was first studied by Ryan and McQueen \cite{ryan1989dynamic, ryan1990dynamic, ryan1990flow}.
They observed the appearance of an inflection point on the $\theta(\sigma)$ curve before the peak stress $\sigma_p$ and attributed the beginning of DRX and the critical conditions to this point.
Later, Poliak and Jonas \cite{Poliak-1996,Poliak-2003,Poliak-2003-2,jonas2003critical} confirmed the hypothesis of DRX describing the inflection point by demonstrating that it is associated with thermodynamic energy released during dislocation movements and the combination between the current dislocations with the previous one leads to the DRX's initiation.
Najafizadeh and Jonas \cite{Najafizadeh-2006} simplified Poliak and Jonas' thermodynamic model using an analytical technique to determine the critical conditions for initiating DRX.
Their widely-used approach relies on a third-degree polynomial to describe the curve $\theta(\sigma)$ and the second derivative to identify the critical stress $\sigma_c$ and strain $\varepsilon_c$.
Once calculated, the critical conditions serve as input data for the Johnson-Mehl-Avrami-Kolmogorov (JMAK) model \cite{Avrami-1939}.
This model is commonly used to estimate the volume fraction of dynamic recrystallization $X_{drx}$ during hot working.
Li \eal \cite{li2015experimental} investigated the DRX properties of micro-alloyed plastic molding steel by using the Avrami kinetics model equation and the Estrin and Mecking mathematical model \cite{estrin1984unified,mecking1981kinetics} to determine the Avrami equation coefficients.

Zhang \eal \cite{zhang2016kinetics} investigated the DRX behaviors of a medium carbon alloy (Cr-Ni-Mo steel) using the Avrami kinetics model equation.
They qualitatively characterized the metallurgical properties based on variations in the Zener-Hollomon parameter.
Cho \eal \cite{cho2005prediction} and Razali \eal \cite{razali2021new} used a well-established model to predict the microstructure evolution of a Mn alloy, with a focus on DRX and grain growth phenomena.
Their results showed consistency with multiple compression tests.
Wan \eal \cite{wan2017experimental} employed the same equation to predict the microstructure evolution of TiAl-based alloys during hot compression.
Li \eal \cite{li2018finite} validated the reliability of the Avrami kinetics model equation when testing the compression of Inconel 718 bolts.
Cui \eal \cite{cui2016hot} analyzed DRX by applying the Avrami kinetics model equation and discovered that the $\beta$-solidifying TiAl alloy usually started evolving at triple joints boundaries before affecting the lamellae.
Recently, Chen \eal \cite{chen2023finite} conducted a Finite Element Analysis of DRX, based on GCr15 (52100 steel) microstructure analysis, and found that temperature and strain rate have a significant impact on DRX initiation.

@@

Dynamic recrystallization is a significant phenomenon for regulating a material's microstructure and mechanical properties during hot working.
In some materials like aluminum, DRX can counterbalance work hardening, leading to a rapid emergence of a plateau.
However, in many austenitic steels, the kinetics of restoration are feeble, causing DRX to activate at a critical strain accumulation condition.
Due to DRX's significant impact on the material's flow stress at high temperatures, it unavoidably affects the material's microstructure following hot working.
Therefore, it is critical to accurately predict the start of DRX to effectively characterize the material.
Several factors, such as the chemical composition of the material, the grain size before deformation, the mode of deformation, and the physical parameters (strain rate, temperature, and strain) condition dynamic recrystallization (DRX), can only be triggered once the critical deformation is reached and can be determined via metallography.
However, this technique necessitates extensive sampling of the pre- and post-critical deformation.
In addition, during the cooling phase, phase transformations can occur that alter the deformed structure as it descends from the hot working temperature, making metallography analysis difficult.
Hence simpler techniques, like developing analytical models have been implemented.
Several studies analyzing the initiation of DRX have been conducted with this objective in mind.

In this paper, we will use the Johnson-Mehl-Avrami-Kohnogorov (JMAK) phenomenological model \cite{Avrami-1939} to calculate the development of Dynamic Recrystallization (DRX) of the material during deformation.
The information obtained from the Gleeble thermosimulator will be used to identify the material flow law and the parameters of the JMAK model.
We obtain the parameters of the JMAK model through a two-step process.
First, critical stresses and strains are determined using the ANN model to filter curves effectively.
Then, these critical values are used as input data to calculate parameters in the JMAK model, with the goal of predicting the volume fraction of dynamic recrystallization.

@@

To improve the results obtained through the process of identifying critical values, we suggest employing the universal approximator capability of artificial neural networks.
This can be Done ! by characterizing each strain-hardening curve using an ANN with just one input (strain) and one output (stress).
In this type of network, each layer of neurons is linked to the preceding and subsequent layers through weighted connections.
Any hidden layer $k$, containing $n$ neurons, takes a weighted sum of the outputs $\overrightarrow{\hat{y}}$ of the immediately preceding layer $(k-1)$, containing $m$ neurons, given by the following~equation:
\begin{equation}
y_i\lay{k} = \sum_{j=1}^m w_{ij}\lay{k} \hat{y}_j^{(k-1)}+ b_i\lay{k},\label{eq:ANN1}
\end{equation}
where $y_i\lay{k}$ is the entry of the $i$th neuron of layer $k$, $\hat{y}_j\lay{k-1}$ is the output of the $j$th neuron of layer $(k-1)$, $w_{ij}\lay{k}$ is the associated weight parameter between the $i$th neuron of layer $k$ and the $j$th neuron of layer $(k-1)$, and $b_i\lay{k}$ is the associated bias of the $i$th neuron of layer $k$.
Those weights $w_{ij}$ and bias $b_i$, for each layer, are the training parameters of the ANN, which we have to adjust during the training procedure.
For the proposed model, we selected the Sigmoid activation function, so that each neuron in the hidden layer $k$ provides an output value ${\hat{y}}$ from the input value $y$ of the same neuron defined by Equation (\ref{eq:ANN1}) according to the following equation:
\begin{equation}
\hat{y}=\frac{1}{1 + \e{-y}}\label{eq:ANN2}
\end{equation}

@@

\begin{figure}[H]
\centering
\includegraphics[width=0.7\columnwidth]{Figures/AnnFit}
\caption{Filtering of the stress/strain data using the ANN for $\mdot\varepsilon=0.001~\ps$ and $T=1050\celsius$.}
\label{fig:AnnFit}
\end{figure}
The models' accuracy and predictive ability are typically evaluated using specific coefficients, such as the mean absolute relative error ($\MARE$), as defined by the following equation:
\begin{equation}
\MARE(\%) = \frac{1}{N} \sum_{i=1}^{N}{\left|\frac{\sigma_i^p -\sigma_i^e}{\sigma_i^e}\right|} \times 100, \label{eq:AARE}
\end{equation}
and the root-mean-squared error ($\RMSE$) defined by the following equation:
\begin{equation}
\RMSE (\MPa) = \sqrt{\frac{1}{N} \sum_{i=1}^{N} \left(\sigma_i^p - \sigma_i^e\right)^2}, \label{eq:RMSE}
\end{equation}
where $\sigma_i^e$ is the experimental value, $\sigma_i^p$ is the value of the stress $\sigma$ predicted using the given model, and $N$ is the total number of data points used to compute those coefficients.
For the proposed ANN filter $\RMSE=0.093~\MPa$ and $\MARE=0.231~\%$, while using a $11^{th}$ order polynomial fit of the experimental data leads to $\RMSE=0.120~\MPa$ and $\MARE=0.275~\%$.

@@

The flow stress curve of the material is influenced by the rate of work hardening, which in turn is affected by dislocations within the free grains.
The predicted volume fraction of the dynamic recrystallization ($X_{drx}^{p}$) is estimated using the Avrami model \cite{wan2017experimental}, commonly known as the JMAK model, expressed by the following equation:
\begin{equation}
X_{drx}^{p} = 1 - \exp\left[ -k\left(\frac{\varepsilon - \varepsilon_c}{\varepsilon_p}\right)^{n_k}\right]
\label{eq:drxpred}
\end{equation}
With $\varepsilon_c$ and $\varepsilon_p$ as the critical and peak strain respectively; $k$ and $n_k$ as the model's parameters and the experimental equivalence of this volume fraction of DRX is given by :
\begin{equation}
X_{drx}^{e} = \frac{\sigma_p-\sigma}{\sigma_p-\sigma_{s}}
\label{eq:drxexp}
\end{equation}

Where $\sigma_p$ and $\sigma_s$ are the peak stress and the steady stress after the peak stress respectively.
The steady stress is considered as the minimum one after the peak stress.
It is possible to establish a dependency relationship between these specific stresses/strains and the Zener-Hollomon parameter $Z = \mdot\varepsilon \exp{\left(\frac{Q}{RT}\right)} \label{eq:ArZ}$, according to the following equation \cite{chen2014dynamic,li2019effect,wang2021artificial}:
\begin{equation}
\begin{cases}
\varepsilon_c = A_cZ^{n_c} \\ \varepsilon_p = A_pZ^{n_p} \\ \sigma_c = B_cZ^{m_c} \\ \sigma_p = B_pZ^{m_p}\\ \sigma_s = B_sZ^{m_s}
\end{cases}
\label{eq:paramsZ}
\end{equation}
With the parameters $A_c$, $A_p$, $n_c$, $n_p$, $B_c$, $B_p$, $B_s$, $m_c$, $m_p$, and $m_s$, the specific strains and stresses' dependency on the Zener-Hollomon parameter whose identification is described in this paper later.

@@

As stated in the research conducted by Tize Mha \eal \cite{TizeMha-2023}, the Johnson--Cook, Zerilli--Armstrong, or Hansel--Spittel models provide an estimate of material behavior at strain rates exceeding $1~\ps$, but they neglect the softening due to DRX that is evident on experimental curves for strain rates below $1~\ps$, as presented in Figure \ref{fig:RawData}.
Indeed, at the lowest strain rates, the flow stress $\sigma$ increases with strain $\varepsilon$ until reaching a value of roughly $\varepsilon=0.2$ to $0.3$.
Afterward, it decreases, maintaining a relatively constant value until the end of the compression test.
The Arrhenius model is the only one that can somewhat explain this softening at low strain rates.
As proposed by Pantalé \eal \cite{Pantale-2021, Pantale-2023} and Tize Mha \eal \cite{TizeMha-2023}, an effective alternative is to use a flow law defined by an artificial neural network trained directly on experimental data from compression tests.
Properly defining the hyper-parameters of this neural network, such as the number of hidden layers, number of neurons, and activation functions, enables us to obtain a flow law that accurately replicates the data acquired from compression tests.

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\authorcontributions{
Conceptualization, P.T.M. and O.P.;
methodology, O.P.;
software, P.T.M. and O.P.;
validation, O.P.;
formal analysis, O.P. and P.D.;
investigation, P.D.;
resources, P.D. and M.J.;
data curation, P.T.M. and P.D.;
writing---original draft preparation, O.P. and P.T.M.;
writing---review and editing, O.P.;
visualization, O.P.;
supervision, M.J., A.T. and O.P.;
project administration, M.J.;
funding acquisition, M.J.
All authors have read and agreed to the published version of the manuscript.}

>>>>

As the occurence of the DRX softens the material, the deformation loads during hot deformation must be adjusted from one pass to another to have more accurate prediction of DRX.
Therefore, understanding the critical conditions for dynamic recrystallization (DRX) is important for modeling industrial processes.
However, the extent of DRX is influenced by factors such as material composition, deformation temperature, strain rate, and strain.
By optimizing the parameters, engineers can attain the desired microstructures and mechanical properties in the final product.
Various experimental techniques have been proposed by researchers to establish DRX's critical conditions such as metallographic analysis \cite{babu2022implication, khan2021interactions}.
However, this technique requires extensive sampling before and after reaching the critical deformation point at which the material experiences recovery and recrystallization processes, resulting in the formation of new grains and a decrease in the average grain size.
Additionally, the cooling phase sometimes entails phase changes (depending the material's type) from the hot working temperature, which alter the deformed structure, rendering the metallographic analysis complex.
Hence, simpler techniques such as the development of analytical models are required to determine DRX initiation.
In this regard, multiple studies have been carried out aiming to analytically identify the initiation of DRX.
For instance, Yan Peng \eal \cite{peng2022dynamic} determined the critical strain and critical stress for the DRX's initiation based on the method proposed by Najafizadeh and Jonas \cite{Najafizadeh-2006} to establish a DRX kinetic model for the hot-rolled condition based on the relationship between the characteristic parameters of DRX and temperature and strain rate. This approach defines the critical stress required for the initiation of DRX during deformation.
According to Gottstein \eal \cite{gottstein2004prediction}, the critical strain for initiating DRX can also be predicted based on a work hardening model of dislocation density.
The onset of dynamic recrystallization (DRX) may be identified through the inflection point in the strain hardening rate $\theta(\sigma)=\frac{\partial \sigma}{\partial \varepsilon}$ where $\sigma$ is the stress and $\varepsilon$ is the strain.

The DRX phenomenon, based on the inflection point, was first studied by Ryan and McQueen \cite{ryan1989dynamic, ryan1990dynamic, ryan1990flow}.
They observed the appearance of an inflection point on the $\theta(\sigma)$ curve before the peak stress $\sigma_p$ and attributed the beginning of DRX and the critical conditions to this point.
Later, Poliak and Jonas \cite{Poliak-1996,Poliak-2003,Poliak-2003-2,jonas2003critical} confirmed the hypothesis of DRX describing the inflection point by demonstrating that it is associated with thermodynamic energy released during dislocation movements and the combinaison between the current dislocations with the previous one leads to the DRX's initiation.
Najafizadeh and Jonas \cite{Najafizadeh-2006} simplified Poliak and Jonas' thermodynamic model using an analytical technique to determine the critical conditions for initiating DRX.
Their widely-used approach relies on a third-degree polynomial to describe the curve $\theta(\sigma)$ and the second derivative to identify the critical stress $\sigma_c$ and strain $\varepsilon_c$.
Once calculated, the critical conditions serve as input data for the Johnson-Mehl-Avrami-Kolmogorov (JMAK) model \cite{Avrami-1939}.
This model is commonly used to estimate the volume fraction of dynamic recrystallization $X_{drx}$ during hot working.
Li \eal \cite{li2015experimental} investigated the DRX properties of micro-alloyed plastic molding steel by using the Avrami kinetics model equation and the Estrin and Mecking mathematical model \cite{estrin1984unified,mecking1981kinetics} to determine the Avrami equation coefficients.

Zhang \eal \cite{zhang2016kinetics} investigated the DRX behaviors of a medium carbon alloy (Cr-Ni-Mo steel) using the Avrami kinetics model equation.
They qualitatively characterized the metallurgical properties based on variations in the Zener-Hollomon parameter.
Cho \eal \cite{cho2005prediction} and Razali \eal \cite{razali2021new} used a well-established model to predict the microstructural evolution of a Mn alloy, with a focus on DRX and grain growth phenomena.
Their results showed consistency with multiple compression tests.
Wan \eal \cite{wan2017experimental} employed the same equation to predict the microstructural evolution of TiAl-based alloys during hot compression.
Li \eal \cite{li2018finite} validated the reliability of the Avrami kinetics model equation when testing the compression of Inconel 718 bolts.
Cui \eal \cite{cui2016hot} analyzed DRX by applying the Avrami kinetics model equation and discovered that the $\beta$-solidifying TiAl alloy usually started evolving at triple joints boundaries before affecting the lamellae.
Recently, Chen \eal \cite{chen2023finite} conducted a Finite Element Analysis of DRX, based on GCr15 (52100 steel) microstructure analysis, and found that temperature and strain rate have a significant impact on DRX initiation.

@@

\textcolor{red}{Dynamic recrystallization is a significant phenomenon for regulating a material's microstructural and mechanical properties during hot working.
In some materials like aluminum, DRX can counterbalance work hardening, leading to a rapid emergence of a plateau.
However, in many austenitic steels, the kinetics of restoration are feeble, causing DRX to activate at a critical strain accumulation condition.
Due to DRX's significant impact on the material's flow stress at high temperatures, it unavoidably affects the material's microstructure following hot working.
Therefore, it is critical to accurately predict the start of DRX to effectively characterize the material.
Several factors, such as the chemical composition of the material, the grain size before deformation, the mode of deformation, and the physical parameters (strain rate, temperature, and strain) condition dynamic recrystallization (DRX), can only be triggered once the critical deformation is reached and can be determined via metallography.
However, this technique necessitates extensive sampling of the pre- and post-critical deformation.
In addition, during the cooling phase, phase transformations can occur that alter the deformed structure as it descends from the hot working temperature, making metallographic analysis difficult.
Hence simpler techniques, like developing analytical models have been implemented.
Several studies analyzing the initiation of DRX have been conducted with this objective in mind}.

\textcolor{red}{In this paper, we will use the Johnson-Mehl-Avrami-Kohnogorov (JMAK) phenomenological model \cite{Avrami-1939} to calculate the development of Dynamic Recrystallization (DRX) of the material during deformation.
The information obtained from the Gleeble thermosimulator will be used to identify the material flow law and the parameters of the JMAK model.
We obtain the parameters of the JMAK model through a two-step process.
First, critical stresses and strains are determined using the ANN model to filter curves effectively.
Then, these critical values are used as input data to calculate parameters in the JMAK model, with the goal of predicting the volume fraction of dynamic recrystallization}.

@@

To improve the results obtained through the process of identifying critical values, we suggest employing the universal approximator capability of artificial neural networks.
This can be done by characterizing each strain-hardening curve using an ANN with just one input (strain) and one output (stress).
In this type of network, each layer of neurons is linked to the preceding and subsequent layers through weighted connections.
Any hidden layer $k$, containing $n$ neurons, takes a weighted sum of the outputs $\overrightarrow{\hat{y}}$ of the immediately preceding layer $(k-1)$, containing $m$ neurons, given by the following~equation:
\begin{equation}
y_i\lay{k} = \sum_{j=1}^m w_{ij}\lay{k} \hat{y}_j^{(k-1)}+ b_i\lay{k},\label{eq:ANN1}
\end{equation}
where $y_i\lay{k}$ is the entry of the $i$th neuron of layer $k$, $\hat{y}_j\lay{k-1}$ is the output of the $j$th neuron of layer $(k-1)$, $w_{ij}\lay{k}$ is the associated weight parameter between the $i$th neuron of layer $k$ and the $j$th neuron of layer $(k-1)$, and $b_i\lay{k}$ is the associated bias of the $i$th neuron of layer $k$.
Those weights $w_{ij}$ and bias $b_i$, for each layer, are the training parameters of the ANN, which we have to adjust during the training procedure.
For the proposed model, we selected the Sigmoid activation function, so that each neuron in the hidden layer $k$ provides an output value ${\hat{y}}$ from the input value $y$ of the same neuron defined by Equation (\ref{eq:ANN1}) according to the following equation:
\begin{equation}
\hat{y}=\frac{1}{1 + \e{-y}}\label{eq:ANN2}
\end{equation}

@@

\begin{figure}[H]
\centering
\includegraphics[width=0.7\columnwidth]{Figures/AnnFit}
\caption{Filtrage des données de contrainte/déformation à l'aide du réseau de neurones artificiels (ANN) pour $\mdot\varepsilon=0.001~\text{s}^{-1}$ et $T=1050\celsius$.}
\label{fig:AnnFit}
\end{figure}
The models' accuracy and predictive ability are typically evaluated using specific coefficients, such as the mean absolute relative error ($\MARE$), as defined by the following equation:
\begin{equation}
\MARE(\%) = \frac{1}{N} \sum_{i=1}^{N}{\left|\frac{\sigma_i^p -\sigma_i^e}{\sigma_i^e}\right|} \times 100, \label{eq:AARE}
\end{equation}
and the root-mean-squared error ($\RMSE$) defined by the following equation:
\begin{equation}
\RMSE (\MPa) = \sqrt{\frac{1}{N} \sum_{i=1}^{N} \left(\sigma_i^p - \sigma_i^e\right)^2}, \label{eq:RMSE}
\end{equation}
where $\sigma_i^e$ is the experimental value, $\sigma_i^p$ is the value of the stress $\sigma$ predicted using the given model, and $N$ is the total number of data points used to compute those coefficients.
For the proposed ANN filter $\RMSE=0.093~\MPa$ and $\MARE=0.231~\%$, while using a $11^{th}$ order polynomial fit of the experimental data leads to $\RMSE=0.120~\MPa$ and $\MARE=0.275~\%$.

@@

The flow stress curve of the material is influenced by the rate of work hardening, which in turn is affected by dislocations within the free grains.
The predicted volume fraction of the dynamic recrystallization ($X_{drx}^{p}$) is estimated using the Avrami model \cite{Avrami-1939} , commonly known as the JMAK model, expressed by the following equation:
\begin{equation}
X_{drx}^{p} = 1 - \exp\left[ -k\left(\frac{\varepsilon - \varepsilon_c}{\varepsilon_p}\right)^{n_k}\right]
\label{eq:drxpred}
\end{equation}
With $\varepsilon_c$ and $\varepsilon_p$ as the critical and peak strain respectively; $k$ and $n_k$ as the model's parameters and the experimental equivalence of this volume fraction of DRX is given by :
\begin{equation}
X_{drx}^{e} = \frac{\sigma_p-\sigma}{\sigma_p-\sigma_{s}}
\label{eq:drxexp}
\end{equation}

Where $\sigma_p$ and $\sigma_s$ are the peak stress and the steady stress after the peak stress respectively.
The steady stress is considered as the minimum one after the peak stress.
It is possible to establish a dependency relationship between these specific stresses/strains and the Zener-Hollomon parameter $Z = \mdot\varepsilon \exp{\left(\frac{Q}{RT}\right)} \label{eq:ArZ}$ \cite{zener1944effect}, according to the following equation as described in \cite{chen2014dynamic,li2019effect,wang2021artificial} :
\begin{equation}
\begin{cases}
\varepsilon_c = A_cZ^{n_c} \\ \varepsilon_p = A_pZ^{n_p} \\ \sigma_c = B_cZ^{m_c} \\ \sigma_p = B_pZ^{m_p}\\ \sigma_s = B_sZ^{m_s}
\end{cases}
\label{eq:paramsZ}
\end{equation}
With the parameters $A_c$, $A_p$, $n_c$, $n_p$, $B_c$, $B_p$, $B_s$, $m_c$, $m_p$, and $m_s$, the specific strains and stresses' dependency on the Zener-Hollomon parameter whose identification is described in this paper later and the effective activation energy parameter $Q$ value is $437.385$ kJ.mol$^{-1}$.

@@

As stated in the research conducted by Tize Mha \eal \cite{TizeMha-2023}, the Johnson--Cook, Zerilli--Armstrong, or Hansel--Spittel models provide an estimate of material behavior at strain rates exceeding $1~\ps$, but they neglect the softening due to DRX that is evident on experimental curves for strain rates below $1~\ps$, as presented in Figure \ref{fig:RawData}.
Indeed, at the lowest strain rates, the flow stress $\sigma$ increases with strain $\varepsilon$ until reaching a value of roughly $\varepsilon=0.2$ to $0.3$.
Afterward, it decreases, maintaining a relatively constant value until the end of the compression test.
The Arrhenius model is the only one that can somewhat explain this softening at low strain rates.
As proposed by Pantalé \eal \cite{Pantale-2021, Pantale-2023} and Tize Mha \eal \cite{TizeMha-2023}, an effective alternative is to use a flow law defined by an artificial neural network trained directly on experimental data from compression tests.
Properly defining the hyperparameters of this neural network, such as the number of hidden layers, number of neurons, and activation functions, enables us to obtain a flow law that accurately replicates the data acquired from compression tests.

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\authorcontributions{
Conceptualization, P.T.M. and O.P.;
methodology, O.P.;
software, P.T.M. and O.P.;
validation, O.P.;
formal analysis, O.P.;
investigation, P.D.;
resources, P.D. and M.J.;
data curation, P.T.M. and P.D.;
writing---original draft preparation, P.T.M.;
writing---review and editing, O.P.;
visualization, O.P.;
supervision, M.J., A.T. and O.P.;
project administration, M.J.;
funding acquisition, M.J.
All authors have read and agreed to the published version of the manuscript.}
